### 2018-07-16 paper/squad-overlay-design.tex
Changes disposition of design

\subsection{The \squad Overlay} 
\label{sec:squad_overlay}

>>>>

\subsection{\Acf*{SPORES}}
\label{sec:squad_overlay}

Above we made the usual assumption that Alice and Bob are represented by one 
device each.
Nowadays this is not the case: they both have multiple devices.
This means that Bob can receive Alice's message \(m\) on several alternative 
devices.
This might not be that problematic, so we will modify our scenario slightly:
The message \(m\) that Alice wants to send to Bob is too large to successfully 
pass every layer of the route.
\Eg each device goes offline and back online every \(t\) time units, the 
bandwidth is \(w\) size units per time unit and the message is \(l\) size 
units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
device will go offline before relaying it to the next node.
The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
where \(l/n\leq w t\).
The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
different devices.

\commentDaniel{We should discuss this problem and outline our solution.}
\commentDaniel{We must edit what's below, it's as before.}
